---
title: "Preliminary Results"
author: "Group 3"
date: "April 25, 2016"
output:
  pdf_document:
    fig_caption: yes
---



```{r connect,echo=FALSE,warning=FALSE,message=FALSE}

setwd("..")

library(RMySQL)
library(ggplot2)
library(dplyr)
library(tidyr)
library(plm)
library(knitr)
library(R.utils)
library(stargazer)
library(xtable)
library(ggmap)

opts_chunk$set(fig.height=8,fig.width=8,warning=FALSE,echo=FALSE,message=FALSE)

sourceDirectory("functions/",modifiedOnly = FALSE)



user_days <- read.csv("data/user_days.csv")


```


We calculate two types of time fixed effect models that use differently specified tweet dummies. In table 1, the dummies are switched on on the day the user receives a tweet and stay on. In table 2, they are switched on as before, but switched off when the user receives a subsequent tweet.

We test the joint significance of all negative tweets (tweets 2,5,6 and 7).

We model the effects of the tweet dummies for a list of dependent variables such that

\[ y_{it} = \beta_1 T1_{it} + \beta_2 T2_{it} + \beta_3 T3_{it} + \beta_4 T4_{it} + \beta_5 T5_{it} + \beta_6 T6_{it} + \beta_7 T7_{it} + \alpha_{t} + u_{it}  \]

```{r echo=FALSE,message=FALSE,warning=FALSE,results="asis",cache=TRUE}

ud <- plm.data(user_days,c("user_id","date"))

ind <- duplicated(ud[,1:2])

ud <- ud[!ind,]

depvars <- c("like_n","tweet_n","trump_rt_n",
             "trump_mention_n","MAGA_n",
             "trump_keyword_n")

models <- list()

ftests <- c("F-Test (Negative Tweets)")
fp <- c("Pr(>F) (Negative Tweets)")

i <- 0
for (depvar in depvars) {
  i <- i + 1
  ud[,"y"] <- ud[,depvar]
  model <- plm(
    y ~ tweet1 + 
      tweet2 + 
      tweet3 + 
      tweet4 + 
      tweet5 +
      tweet6 +
      tweet7, 
    data=ud, 
    #index=c("user_id","date"),
    model = "within", 
    effect = "time"
  )
  assign(paste0("m_",depvar),model)

  f <- round(lmtest::waldtest(model,c("tweet2","tweet5","tweet6","tweet7"),test="F")[2,3],3)
  fpi <- round(lmtest::waldtest(model,c("tweet2","tweet5","tweet6","tweet7"),test="F")[2,4],3)
  ftests <- c(ftests,f)
  fp <- c(fp,fpi)
}


stargazer::stargazer(
  m_like_n,m_tweet_n,m_trump_rt_n,m_trump_mention_n,m_MAGA_n,m_trump_keyword_n,
  column.labels = c("likes","tweets","retweets","mentions","MAGA","keywords"),
  add.lines=list(ftests,fp),
  header=FALSE
)

```



```{r echo=FALSE,message=FALSE,warning=FALSE,results="asis",cache=TRUE}


depvars <- c("like_n","tweet_n","trump_rt_n",
             "trump_mention_n","MAGA_n",
             "trump_keyword_n")

models <- list()

ftests <- c("F-Test (Negative Tweets)")
fp <- c("Pr(>F) (Negative Tweets)")

i <- 0
for (depvar in depvars) {
  i <- i + 1
  ud[,"y"] <- ud[,depvar]
  model <- plm(
    y ~ temptweet1 + 
      temptweet2 + 
      temptweet3 + 
      temptweet4 + 
      temptweet5 +
      temptweet6 +
      temptweet7, 
    data=ud, 
    #index=c("user_id","date"),
    model = "within", 
    effect = "time"
  )
  assign(paste0("m_",depvar),model)

  f <- round(lmtest::waldtest(model,c("temptweet2","temptweet5","temptweet6","temptweet7"),test="F")[2,3],3)
  fpi <- round(lmtest::waldtest(model,c("temptweet2","temptweet5","temptweet6","temptweet7"),test="F")[2,4],3)
  ftests <- c(ftests,f)
  fp <- c(fp,fpi)
}


stargazer::stargazer(
  m_like_n,m_tweet_n,m_trump_rt_n,m_trump_mention_n,m_MAGA_n,m_trump_keyword_n,
  column.labels = c("likes","tweets","retweets","mentions","MAGA","keywords"),
  add.lines=list(ftests,fp),
  header=FALSE
)

```


For simplicity, we also run t-tests comparing the means of the treatment and control groups during the time when tweets were being sent out

```{r}

treatment_period <- user_days %>%
  mutate(date_d = as.Date(date_d)) %>%
  filter(date_d >= "2016-04-14" & date_d < "2016-05-04")


for (y in depvars) {
  print(y)
  test <- t.test(
  treatment_period[treatment_period$t_group=="T",y],
  treatment_period[treatment_period$t_group=="C",y]
  )
  print(test)
}

treatment_summary <- treatment_period %>%
  group_by(t_group)

```

